Verifying Demonstrations

### 2020-03-11 paper/DB-Schnorr-nbit.tex
Adds nbit MF proof

>>>>

\subsection{\acs*{DBMF}, \acs*{DBTF} and \acs*{DBDH} resistance}

\paragraph{\Acl{DBMF}}

In \ac{DBMF}, the adversary will try to authenticate to a verifier by querying 
a far-away prover.
By \cref{TaintedMF}, pure relaying will be detected by the verifier.
So the adversary must resort to things like querying in advance \etc.

\begin{theorem}[\acs*{DBMF} resistance]
  Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-MF adversary, then 
  \(\Adv_{\DBS}^{\text{MF}}(\adv) = \frac{1}{2^n}\), where \(m, q\) are as in 
  \cref{DB-Schnorr}.
\end{theorem}

\begin{proof}
  It follows from the \ac{ZK} property (\cref{UWB-ZKPK}) that the adversary 
  cannot learn anything by observation.
  This leaves the adversary with two options:
  \begin{enumerate}
  \item guess which challenge the verifier will use and request the correct 
    response from the prover, receiving the challenge first would taint the 
    session (\cref{TaintedMF});
  \item guess the response.
  \end{enumerate}

  The first option yields success with probability \(\frac{1}{2}\), since the 
  choice is uniformly distributed over the two challenges.

  The second option yields a lower success probability:
  Assume that each bit reveals some information about the future bits.
  The first bit must still be guessed, this is yields a probability of \emph{at 
  most} \(\frac{1}{2}\).

  The best strategy is to guess which challenge the verifier will select.
  Thus, the success probability is \(\frac{1}{2}\) per round, or 
  \(\frac{1}{2^n}\) in total.
\end{proof}
